**Density Dependence**

### 2023-02-13 Rmd/omMac.Rmd
added Prod Curve to DD plots

d2=model.frame(FLQuants(vpaDDM[,"2050"],"Biomass"=function(x) biomass(x),"SSB"=function(x) ssb(x),
                                        "F"=function(x) fbar(x),"Yield"=function(x) catch(x)),drop=T)
p4=ggplot(d2)+
  geom_line(aes(SSB,Yield))

@@

d3=model.frame(FLQuants(vpaDDMM[,"2050"],"Biomass"=function(x) biomass(x),"SSB"=function(x) ssb(x),
                                         "F"=function(x) fbar(x),"Yield"=function(x) catch(x)),drop=T)
p4=ggplot(d3)+
  geom_line(aes(SSB,Yield))

@@

d4=model.frame(FLQuants(vpaDDMMM[,"2050"],"Biomass"=function(x) biomass(x),"SSB"=function(x) ssb(x),
                                          "F"=function(x) fbar(x),"Yield"=function(x) catch(x)),drop=T)
p4=ggplot(d4)+
  geom_line(aes(SSB,Yield))

>>>>

d2=model.frame(FLQuants(vpaDDM[,"2050"],"Biomass"=function(x) biomass(x),"SSB"=function(x) ssb(x),
                                        "F"=function(x) fbar(x),"Yield"=function(x) catch(x)),drop=T)
p4=ggplot(d2)+
  geom_line(aes(SSB,Yield))+
  geom_line(aes(SSB,Yield),col="red",data=d1)

@@

d3=model.frame(FLQuants(vpaDDMM[,"2050"],"Biomass"=function(x) biomass(x),"SSB"=function(x) ssb(x),
                                         "F"=function(x) fbar(x),"Yield"=function(x) catch(x)),drop=T)
p4=ggplot(d3)+
  geom_line(aes(SSB,Yield))+
  geom_line(aes(SSB,Yield),col="red",data=d1)

@@

d4=model.frame(FLQuants(vpaDDMMM[,"2050"],"Biomass"=function(x) biomass(x),"SSB"=function(x) ssb(x),
                                          "F"=function(x) fbar(x),"Yield"=function(x) catch(x)),drop=T)
p4=ggplot(d4)+
  geom_line(aes(SSB,Yield))+
  geom_line(aes(SSB,Yield),col="red",data=d1)

### 2023-02-13 Rmd/omWhb.Rmd
added Prod Curve to DD plots

d1=model.frame(FLQuants(vpaM[,"2050"],"Biomass"=function(x) biomass(x),"SSB"=function(x) ssb(x),
                                      "F"=function(x) fbar(x),"Yield"=function(x) catch(x)),drop=T)
d=rbind(cbind("What"="ICES",dices),
        cbind("What"="VPA",dvpa),
        cbind("What"="M",d1))
ggplot(d)+
  geom_line(aes(SSB,Yield,col=What))
```

>>>>

d1=model.frame(FLQuants(vpaM[,"2050"],"Biomass"=function(x) biomass(x),"SSB"=function(x) ssb(x),
                                      "F"=function(x) fbar(x),"Yield"=function(x) catch(x)),drop=T)
d=rbind(cbind("What"="ICES",dices),
        cbind("What"="VPA",dvpa),
        cbind("What"="M",d1))
ggplot(d)+
  geom_line(aes(SSB,Yield,col=What))+
  geom_line(aes(SSB,Yield),col="red",data=d1)

```
